Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-19 paper/ijcai/paper.tex
more polishing intro
polishing

The contributions of this work are the following ones:
\begin{itemize}
	\item A comprehensive study on the combination of \sfl{} and \ds{}
     for bug localization of \emph{Java} faulty programs.
   \item A tool that implements \comb{}.
\end{itemize}

@@

This section provides details on the proposed approach, \combpar{}, that combines
\sfl{} with \ds{}; it also discusses the oracle problem.

\subsection{Combining \sfl{} and \ds{}}
\label{sec:comb}

>>>>

The contributions of this work are the following ones:
\begin{itemize}
	\item A study, using real-world applications and bugs, on the combination
    of \ds{} and \sfl{} for bug localization of \emph{Java} faulty programs.
   \item A tool that implements \comb{}.
\end{itemize}

@@

This section provides details on the proposed approach, \combpar{}, that combines
\ds{} with \sfl{}; it also discusses the oracle problem.

\subsection{Combining \ds{} and \sfl{}}
\label{sec:comb}
